Distributed multi-objective evolutionary optimization using island-based selective operator application

### 2019-05-13 hpmoon-asoco.tex
Taking care of epistasy from rev #4

Obtained results also show that when increasing the number of islands, the
automatic overlapping method ($A$) significantly improves the results with
respect to the disjoint and overlapped methods. However, this is only
apparent with larger chromosome sizes. Therefore, the length of the
chromosome is also a key factor to take into account in automatic overlapping
methods, and not only the number of islands. 
%Studying this factor with more types of problems, and new configurations of population size and chromosome lengths could be addressed in the future. 
Since our method divides the individuals into blocks of divisible size, aggregation methods after migration, such as the ones used in \cite{Kimovski15Parallel} or \cite{Dorronsoro13superlinear} can be also tested. But as complete individuals \textcolor{blue}{treated} in each island, the possibility of using a real number, such as 0.3 (30\% overlapping) instead an integer value opens future experimental setups.
For example, comparing 
different ways to calculate $c$ using linear, logarithmic or exponential functions
depending on population size, number of islands, or other values, or using some statistical parameter setting method, such as Taguchi's \cite{Keratmatpour2018Taguchi}.

>>>>

Obtained results also show that when the number of islands
\textcolor{blue}{is increased}, the
automatic overlapping method ($A$) significantly improves the results with
respect to the disjoint and overlapped methods. However, this is only
apparent with larger chromosome sizes. Therefore, the length of the
chromosome is also a key factor to take into account in automatic overlapping
methods, and not only the number of islands. 
%Studying this factor with more types of problems, and new configurations of population size and chromosome lengths could be addressed in the future. 
Since our method divides the individuals into blocks of divisible
size, aggregation methods after migration, such as the ones used in
\cite{Kimovski15Parallel} or \cite{Dorronsoro13superlinear} can be
also tested. But as complete individuals \textcolor{blue}{treated} in
each island, the possibility of using a real number, such as 0.3 (30\%
overlapping) instead an integer value opens future experimental
setups. \textcolor{blue}{This should also take care of epistatic
  interactions between chromosome sizes: although variation operators
  operate on chromosome fragments, selection and fitness evaluation
  operates on the whole chromosome; besides, there is migration
  between islands, so the probability of reaching local minima due to
  this fact is, in fact, going to be avoided.}
For example, comparing 
different ways to calculate $c$ using linear, logarithmic or exponential functions
depending on population size, number of islands, or other values, or using some statistical parameter setting method, such as Taguchi's \cite{Keratmatpour2018Taguchi}.
